$N_{\text{eff}}$ priors

### 2015-06-22 Notes/N_eff_prior_paper.tex
adding new marginalization technique

\begin{itemize}
\item We are now using a simplistic lensing noise but I have lensing noise with the usual Hu Okamoto formula. Iterative Seljack not there yet.
\item We are varying $\tau ~ n_{s} ~ A_{s} ~ N_{\rm eff} ~ H_{0}$. The neutrino sector consists of one massive neutrino of $m_{\nu}=0.083$ eV, $\Omega_{\nu}h^{2}=0.0009$
\item Next TODO: Check for bugs and errors code in its early stages. PCA? what prior is more important? Full MCMC should not be extremely hard with cosmosis.
\end{itemize}

@@

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[scale=0.6]{PS_with_noise.pdf}
\caption{CMB power spectrum for our fiducial cosmology together with the instrumental noise used in this work.}
\label{fig:cmb-cl-noise}
\end{center}
\end{figure}

@@

\section{Data}
\section{Results}

>>>>

\begin{itemize}
\item We are now using a simplistic lensing noise but I have lensing noise with the usual Hu Okamoto formula. Iterative Seljack not there yet.
\item We are varying $\tau, ~ n_{s}, ~ A_{s}, ~ N_{\rm eff}, ~ H_{0}, w,~\Omega_{\nu}h^{2},~\Omega_{c}h^{2},~\Omega_{b}h^{2}$. The neutrino sector consists of one massive neutrino of $m_{\nu}=0.083$ eV, $\Omega_{\nu}h^{2}=0.0009$
\item Next TODO: Check for bugs and errors code in its early stages. PCA? what prior is more important? Full MCMC should not be extremely hard with cosmosis.
\end{itemize}

@@

\subsection{Fisher Matrix formalism}
Copied from paper change it for pubblication:

To avoid any possible numerical instability in the marginalising procedure, we calculate the the Fisher matrix marginalised over the standard LCDM parameters following (Albrecht et al. 2009)
\begin{equation}
G = F^{\phi\phi} - F^{\phi\psi}U\Lambda^{-1}U^{T}F^{\phi\psi},
\end{equation}
where we define $\phi = \{N_{eff},...\}$ and $\psi = \{\Omega_{m} ... marginal\}$; therefore, $F^{\phi\phi}$ is the block of the total Fisher matrix containing the parameters we want to constrain, whilst $F^{\psi\psi}$ is the nuisance-parameter Fisher sub-matrix. Here, $\Lambda$ is the diagonal matrix whose elements are the eigenvalues of $F^{\psi\psi}$, whilst U is the orthogonal matrix diagonalising $F^{\psi\psi}$. By using Eq., our marginalising procedure is more stable, since degeneracies in $F^{\phi\phi}$ are properly propagated to G with no instabilities, and we do not even worry about a possibly ill-conditioned $F^{\phi\phi}$ sub-matrix, since we check its stability on the fly by the diagonalisation.

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[scale=0.6]{PS_with_noise.pdf}
\caption{CMB power spectrum for our fiducial cosmology together with the instrumental noise used in this work. They are basically equivalent to a cosmic variance limited experiment with $l_{max}\sim 3000$}
\label{fig:cmb-cl-noise}
\end{center}
\end{figure}

@@

\section{Data}

\begin{table}[htdp]
\caption{Fiducial values used.}
\begin{center}
\begin{tabular}{|c|c|}
\hline
$H_{0}$ &\\
\hline
\hline
$\tau$ &  \\
\hline

\hline
$A_{s}$ & \\
\hline

\hline
$n_{s}$ & \\
\hline

\hline
$N_{eff}$ & \\
\hline
\end{tabular}
\end{center}
\label{default}
\end{table}%

\section{Results}

\begin{table}[htdp]
\caption{How well we do constrain separate parameters with this data without any external prior?}
\begin{center}
\begin{tabular}{|c|c|}
\hline
$H_{0}$ & 0.32\% \\
\hline
\hline
$\tau$ & 2.26 \%\\
\hline

\hline
$A_{s}$ & 0.37 \%\\
\hline

\hline
$n_{s}$ & 0.25 \%\\
\hline

\hline
$N_{eff}$ & 0.9 \%\\
\hline

\end{tabular}
\end{center}
\label{default}
\end{table}%
